### 2015-01-14 fundamentals/intro.tex
rearrange

As nuclear power expands both domestically and internationally, nuclear fuel
cycle performance analysis on technical, economic, political, and environmental
axes increases in importance. Appropriate nuclear fuel cycle analysis requires
calculation of myriad physical, nuclear, chemical, industrial, and political
phenomena. Nuclear fuel cycle simulators therefore couple complex systems such
as nuclear process physics, facility deployment, and material routing.
However, current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly comparison of modeling methodologies. Finally, they result
in over-specification, rendering most tools applicable to only a subset of
desired simulation fidelities, scales, and applications.  A next generation
fuel cycle simulator is needed which incorporates modern insights from
simulation science and software architecture to solve these problems. As a
bonus, many of these methods simultaneously enable more efficient, accurate,
robust, and validated analysis.

The \Cyclus nuclear fuel cycle simulator framework and 
its modeling ecosystem address this need for a next-generation nuclear fuel cycle 
simulator. This dynamic simulator employs discrete agents, time, and isotopic resolution of materials 
and supports a range of analysis types, levels of 
detail, and analyst sophistication.
Additionally, \Cyclus employs a modular architecture and 
open development process that supports user access and 
encourages developer extensions.

Historically, nuclear fuel cycle simulators have estimated 
nuclear fuel cycle performance using software 
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
system dynamics
proprietary models. To date, current tools are either static, fleet-based, 
privately distributed, or all of the above. Each of these qualities presents a 
severe challenge to modeling fidelity, generality, efficiency, robustness, and 
scientific transparency.

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.  
Dynamic nuclear fuel cycle analysis more realistically 
supports a range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
cultivates an ecosystem of modeling and calculation options 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

Historically, the national laboratories have driven development and regulated 
the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{yacout_modeling_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}. 
Outside the national laboratories, researchers have created new nuclear fuel cycle 
simulation tools when existing tools were not available or not sufficiently 
general to calculate their metrics of interest with their method of choice.  
With limited access to the national laboratory tools and a need to customize 
them for research purposes, universities and private industry researchers have 
``reinvented the wheel'' by developing tools of their own from scratch and 
tailored to their own needs, for example \gls{CAFCA}\cite{guerin_impact_2009} and 
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.

This trend has resulted in a proliferation of specialized
fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials in static equilibrium, while 
other simulators capture the dynamics of the system.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials as streams and facilities as fleets, in an aggregated 
fashion. Simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. For example, a simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

>>>>

As nuclear power expands both domestically and internationally, nuclear fuel
cycle performance analysis on technical, economic, political, and environmental
axes increases in importance. Appropriate nuclear fuel cycle analysis requires
calculation of myriad physical, nuclear, chemical, industrial, and political
phenomena. Nuclear fuel cycle simulators therefore couple complex systems such
as nuclear process physics, facility deployment, and material routing.
However, current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly compare modeling methodologies. Finally, they 
over-specialize, rendering most tools applicable to only a subset of
desired simulation fidelities, scales, and applications.
The \Cyclus nuclear fuel cycle simulator framework and 
its modeling ecosystem incorporate modern insights from
simulation science and software architecture to solve these problems. 
As a bonus, many of these methods simultaneously enable more efficient, accurate,
robust, and validated analysis.

The \Cyclus next-generation fuel cycle simulator is the result of design 
choices made explicitly to:
\begin{itemize}
\item support user access and encourages developer extensions,
\item enable plug-and-play comparison of modeling methodologies,
\item and address a range of analysis types, levels of detail, and analyst sophistication.
\end{itemize}

Historically, nuclear fuel cycle simulators have estimated 
nuclear fuel cycle performance using software 
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
system dynamics
proprietary models. To date, current tools are either static, fleet-based, 
privately distributed, or all of the above. Each of these qualities presents a 
severe challenge to modeling fidelity, generality, efficiency, robustness, and 
scientific transparency. 
An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.

\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular 
architecture, an open development process, discrete agents, discrete time, and 
arbitrarily detailed isotopic resolution of materials.  Dynamic nuclear fuel 
cycle analysis more realistically supports a range of simulation goals than 
static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
cultivates an ecosystem of modeling and calculation options 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

However, methods for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials in static equilibrium, while 
other simulators capture the dynamics of the system.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials as streams and facilities as fleets, in an aggregated 
fashion. Simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. For example, a simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

This overspecialization and fractured community is the result of history. 
Historically, the national laboratories have driven development and regulated 
the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{yacout_modeling_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}.  Outside the national laboratories, 
researchers have created new nuclear fuel cycle simulation tools when existing 
tools were not available or not sufficiently general to calculate their metrics 
of interest with their method of choice.  With limited access to the national 
laboratory tools and a need to customize them for research purposes, 
universities and private industry researchers have ``reinvented the wheel'' by 
developing tools of their own from scratch and tailored to their own needs, for 
example \gls{CAFCA}\cite{guerin_impact_2009} and 
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
